### 2016-12-20 paper_gerasimovd.tex
Less macros

\usepackage{cite}
\usepackage{hyperref} % \autoref

\usepackage[pdftex]{graphicx}
\graphicspath{{pic/}}
\usepackage{tikz}

\usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
\usepackage{mathtools}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}

\newcommand{\mcL}{\mathcal{L}} % L2 space
\newcommand{\mcO}{\mathcal{O}} % Big O
\newcommand{\bbC}{\mathbb{C}} % complex plane
\newcommand{\bbD}{\mathbb{D}} % complex unit disk
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbT}{\mathbb{T}} % complex unit circle
\newcommand{\bbH}{\mathbb{H}} % complex upper half plane

% imaginary unit
\newcommand{\iu}{{i\mkern1mu}}

% \renewcommand{\Re}{\operatorname{Re}}
% \renewcommand{\Im}{\operatorname{Im}}

\newcommand{\eexp}[1]{e^{#1}}

\renewcommand{\Re}{\operatorname{Re}}
\renewcommand{\Im}{\operatorname{Im}}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%

@@

\section{Definitions}
\begin{itemize}
\item $\bbC$: complex plane, $\bbC = \{ x + \iu y \mid x, y \in \bbR \}$ 
\item $\bbH$: upper complex half-plane, $\bbH = \{ x + \iu y \mid y > 0, x, y \in \bbR \}$
\item $\bbD$: unit disk, $\bbD = \{ z \mid \abs{z} < 1 \}$
\item $\bbT$: unit circle, $\bbT = \partial \bbD =  \{z \mid \abs{z} = 1 \}$
\item $z$ denotes a complex argument on upper complex half-plane $\bbH$
\item $\zeta$ denotes a complex argument on unit disk $\bbD$
\end{itemize}

@@

Cayley transform maps $\bbH$ to $\bbD$:
\begin{equation}\label{eq:cayley}
W(z) = \frac{z - \iu}{z + \iu}
\end{equation}
, inverse Cayley transform maps $\bbD$ to $\bbH$:
\begin{equation}\label{eq:cayley_inverse}
w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}
\end{equation}

One notable property of the Cayley transform is that it injectively maps $\bbR$ into unit circle $\bbT$.

@@

\begin{theorem}[{\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}]
The following statements are equivalent:
\begin{itemize}
\item the dissipating operator $Z$ is complete
\item
\begin{equation}\label{eq:blaschke}
\lim\limits_{r = 1} \int\limits_{\bbT} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
\end{equation}
\end{itemize}
\end{theorem}

@@

\section{The model}
% TODO http://tex.stackexchange.com/a/155317/5966 ?
\begin{figure}
\centering
\begin{tikzpicture}[scale=1.1] % TODO SCALE!!!
\input{pic/resonator_bundle.tex}
\end{tikzpicture}
\caption{Quantum graph $\Gamma$, consisting of semi infinite edges $\Omega_L, \Omega_R$ and a resonator $\Omega$, consisting of $W$ identical edges of length 1.}
\label{fig:res_bundle}
\end{figure}

@@

Let's use Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, to be precise, it's $\mcL^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}
\le
\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{aligned}
\end{equation}
Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.

>>>>

\usepackage{cite}
\usepackage{hyperref} % \autoref
\usepackage{tikz}
\usepackage{amsmath,amsfonts,amssymb,amsthm,amscd,amsxtra}
\usepackage{mathtools}

\newcommand{\mcO}{\mathcal{O}} % Big O
\newcommand{\iu}{{i\mkern1mu}} % imaginary unit
\newcommand{\eexp}[1]{e^{#1}}  % convenient exponent

\renewcommand{\Re}{\operatorname{Re}} % default Re/Im is weird
\renewcommand{\Im}{\operatorname{Im}}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%

@@

\section{Definitions}
\begin{itemize}
\item $\mathbb{C}$: complex plane, $\mathbb{C} = \{ x + \iu y \mid x, y \in \mathbb{R} \}$ 
\item $\mathbb{H}$: upper complex half-plane, $\mathbb{H} = \{ x + \iu y \mid y > 0, x, y \in \mathbb{R} \}$
\item $\mathbb{D}$: unit disk, $\mathbb{D} = \{ z \mid \abs{z} < 1 \}$
\item $\mathbb{T}$: unit circle, $\mathbb{T} = \partial \mathbb{D} =  \{z \mid \abs{z} = 1 \}$
\item $z$ denotes a complex argument on upper complex half-plane $\mathbb{H}$
\item $\zeta$ denotes a complex argument on unit disk $\mathbb{D}$
\end{itemize}

@@

Cayley transform maps $\mathbb{H}$ to $\mathbb{D}$:
\begin{equation}\label{eq:cayley}
W(z) = \frac{z - \iu}{z + \iu}
\end{equation}
, inverse Cayley transform maps $\mathbb{D}$ to $\mathbb{H}$:
\begin{equation}\label{eq:cayley_inverse}
w(\zeta) = \iu \frac{1 + \zeta}{1 - \zeta}
\end{equation}

One notable property of the Cayley transform is that it injectively maps $\mathbb{R}$ into unit circle $\mathbb{T}$.

@@

Theorem ({\cite[p. 95]{nikol2012treatise}}, {\cite[p. 99]{nikol2012treatise}}):

The following statements are equivalent:
\begin{itemize}
\item the dissipating operator $Z$ is complete
\item
\begin{equation}\label{eq:blaschke}
\lim\limits_{r = 1} \int\limits_{\mathbb{T}} \log \abs{\det S(r \zeta)} d m(\zeta) = 0
\end{equation}
\end{itemize}

@@

\section{The model}
% TODO http://tex.stackexchange.com/a/155317/5966 ?
\begin{figure}
\centering
\begin{tikzpicture}[scale=1.1] % TODO SCALE!!!
\input{resonator_bundle.tex}
\end{tikzpicture}
\caption{Quantum graph $\Gamma$, consisting of semi infinite edges $\Omega_L, \Omega_R$ and a resonator $\Omega$, consisting of $W$ identical edges of length 1.}
\label{fig:res_bundle}
\end{figure}

@@

Let's use Cauchy-Schwarz's inequality:
\[
\big| \langle u,v \rangle \big| \leq \left\|u\right\| \left\|v\right\|
\]
, to be precise, it's $\mathcal{L}^2[a, b]$ version:
\[
\abs{
\int\limits_{t=a}^{b} f(t) g^*(t) dt
}
\le
\sqrt{\int\limits_{t=a}^b \abs{f(t)}^2 dt }
\sqrt{\int\limits_{t=a}^b \abs{g(t)}^2 dt }
\]
% 
To use inequality, we are going to represent the integrand in (\ref{eq:critp}) as $f(t) g^*(t)$ as follows:
\begin{equation}\label{eq:split}
\begin{aligned}
a      &= 0 \\
b      &= 2 \pi \\
f(t)   &= \ln s(R \eexp{\iu t} + \iu C) \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i} \\
g^*(t) &= \frac{\sqrt{R}}{R \eexp{\iu t} + \iu C + i}
\end{aligned}
\end{equation}
Next, we will show that $\norm{g}$ (that is, $\sqrt{\int \abs{g(t)}^2}$) is bounded by a constant which does not depend on $r$, and $\norm{f}$ goes to $0$ as $r$ goes to $1$, hence (\ref{eq:critp}) converges.
